Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-19 response_to_reviewers.tex

First of all, if one runs out of computational resources needed to check the quality of a model, it simply means that the inversion has been poorly planned! I am sure the authors know the number of node hours per forward run very well. It is therefore simply a matter of choosing a minimum period that leaves enough resources to run a reasonable model assessment. Simply saying that you better like to use the INCITE resources to just produce a colorful model, is a miserable excuse that I find completely unacceptable.

Second, it is not clear what to learn from 2 point-spread functions (apart from the fact that they were computed for different data). As the authors demonstrate in section 10 of their manuscript (interpretation and comparison), there are many more than 2 interesting points inside the Earth.

Third, the authors dedicate 13 pages (!!!) to the comparison of their new model to the previous and to other models. However, without any quantitative information on how much the new model has improved, this seems to be a rather meaningless exercise.
}

\response{We welcome scientific criticisms, however it is not acceptable that the reviewer completely ignores the fact that they are targeting a student,
%they is gender neutral
who is the first author of this manuscript.
We believe the reviewer is fully aware of the pitfalls of resolution analysis and uncertainty quantification in all tomographic inversions, unless a Bayesian approach is used, which is not even possible for classical global tomographic inversions.
The reason we did not perform PSF tests was not because we ran out of core-hours but chose not to use them for this purpose,
because a few PSF tests do not say much about global resolution.
%The reason we mentioned the cost of PSF tests in the original manuscript was rather to make the point that despite the cost we will not get the full resolution. Otherwise, the core hours have never been an issue for our INCITE allocations but the ability to handle large data sets in FWI while carefully investigating the model evolution is the main challenge. 
Nevertheless, we added six PSF tests in the revised manuscript and SOM in addition to our existing quantitative comparisons of traveltime and amplitude misfits.
}

@@

\response{
Based on our estimation, there are about 6,000~events in the global CMT catalog suitable for global FWI.
So to say that at 1,480 events our dataset is ``not overwhelming'' seems rather harsh,
even more so if one considers that the only other global FWI efforts,
the Bozdag et al. (2016) and French \& Romanowicz (2015),
used just a few hundred events.
We also emphasize that the information going into the model,
as illustrated in the measurement window density maps shown in Figs.~2--4, is large.
This is another strength of our technique.
}

\rev{(4) I am also quite concerned about the writing and presentation style. The sections on supercomputing sound pretentious, which is a high risk for the authors, given that their model does not tell us many new things about the internal structure of the Earth. 
}

\response{
We did not intend for the sections on supercomputing to sound grandiose; we were merely attempting to convey the computational challenges and how these were overcome.
Much of this work was accomplished by the student first-author of the paper, and we were trying to highlight these rather nontrivial accomplishments.
Nevertheless, also in view of comments by other reviewers and the editor, we have toned down the language in the revised manuscript.

The statement ``their model does not tell us many new things about the internal structure of the Earth'' is again unnecessarily harsh and uncalled for. We already emphasize the advantages of our models, as we believe the reviewer is well aware of. 
For example,
this is one of the few tomographic studies to constrain shear and compressional wavespeeds together in the same frequency band.
Thus, our Vp/Vs ratios certainly add scientific value.
We also invert body and surface waves simultaneously, which is important for constraining upper mantle structure.
Additionally, we make no crustal corrections, 
which too should lead to better constrained images of the deeper Earth.
Finally, in newly added figures visually comparing M15 and M25 numerous new features emerge,
such as several hotspots in the Indian Ocean, etc. 
}

@@

\rev{This manuscript presents GLAD\_M25 (or M25), un update of GLAD\_M15 (or M25) published by Bozdag et al. in 2016. Model M25 is an improvement because it is based on an analysis of 1400 events (250 events were used by Bozdag et al.) and the inversion has progressed by 10 iterations.
It is clear that the authors have thought deeply about the engineering of M25. I appreciate the phenomenal amount of work that has gone into developing M25 but there is unnecessary repetition of topics in Bozdag et al. (i.e., data formatting, earthquake relocation, crustal corrections, work flows, ...).
Figure 2 from Bozdag et al. is copied-and-pasted as Figure 4 in this paper and the graphs of misfit reductions and traveltime delay distributions are essentially updates of similar graphs in Bozdag et al..
}

\response{We have moved Fig.~2 (and numerous other figures) to the SOM. However, the misfit reduction plot is a rather integral part of the paper!}

\rev{I must admit that I am disappointed by the model evaluation in Section 10. The comparison with maps and cross-sections from other tomographic models is somewhat superficial and not as persuasive as the earlier sections of the paper.
}

\response{We have removed all the regional and full global comparisons, leaving just the plumes and slab figures, while adding a discussion of differences between M15 and M25, as requested by other reviewers. Please also see our PSF tests as part of model evaluations in the main text and in the SOM.}

@@

\rev{The manuscript is in decent shape but the writing is somewhat rushed after page 20 or so. The senior authors should polish the text and remove paragraphs, primarily in early sections, on topics that have been covered by Bozdag et al.
The authors don't do the point-spread function analysis so subsection 9.1 can be eliminated. I have annotated the PDF copy to suggest edits and to point out fuzzy wording.
}

\response{We have further polished the writing later in the manuscript
Thanks for the annotated manuscript! We have accommodated most comments and suggestions.
Based on suggestions by the other reviewers,
we added six PSF tests to the manuscript and the supplementary material.}

\rev{The GLAD-M tomography stands out from the other approaches by casting the inverse without compromising the physics of wave propagation. Consequently, the workflow is laborious and iterations are slow. Ten iterations for a moderate data set (compared to the S40RTS data set, for example), took more than two years. Sections 1--9 indicate that the authors are convinced about the value of their approach but the discussion onward from Section 10 is qualitative and not serving the authors' case.
I worry that readers might wonder whether M25 is a significant step forward from M15 and whether the tremendous engineering and use of computer power justifies the (re)discovery of velocity anomalies that do not appear to change our understanding of mantle structure and dynamics.
}

\response{We have modified the manuscript substantially, as discussed previously. We focus more concretely on differences between M15 and M25 to better highlight the power of 10 additional iterations with $>1,400$ events. The ``two-years'' is not just the time spent for 10 iterations but code development and optimization as well as investigations of global FWI to define strategies for how to make progress. This is not a straightforward process as in exploration seismic yet because of the size and complex physics of the entire crust and mantle we have to take into account.
Unfortunately,
comparisons with other models will always be rather qualitative, because we have no way of using such models in 3D wave simulations, mainly because 3D mantle models are difficult to combine with 3D crustal models. Underneath the oceans there tends to be a `gap' between the mantle model and the crust, whereas underneath the continents there tends to be a region of overlap, and this make `gluing' the two together challenging. Thus it may be unfair to assess the models with crustal corrections with 3D numerical wave simulations.}

@@

\rev{I recommend therefore some restructuring of the paper by relating the modeling results to the adjoint tomography approaches. To stay on the topics raised in sections 1--9, I suggest the authors demonstrate with specific examples that the complex GLAD-M workflow is the only viable approach for making progress in global-scale seismic tomography. The paper will become more technical in tone and will cater primarily to the seismological community but that should be acceptable for GJI. Image interpretations in terms of Earth's structure and dynamics could be published in journals with a somewhat broader readership. Restructuring will involve new work for the leading student author, but I think it is worth the effort.
}

\response{We have substantially restructured the manuscript along the lines suggested.}

\rev{1. Recalculation of sensitivity kernels after each iteration is expensive. Is it necessary?
It would be helpful to see examples of how surface wave kernels changed from iteration 0 to 25 for ``simple'' paths (e.g., in ocean basins) and for ``complex'' paths (e.g., along ocean-continent margins). Are there good examples of waveforms that demonstrate that M25 is explaining surface-wave multipathing because kernels are recalculated for a 3-D structure?
}

\response{We do not calculate sensitivity kernels, as in the Dahlen \& Nolet banana-doughnut approach! Instead, we directly calculate contributions to the model gradient, which involves assimilation of the measurements for the current model. Thus, this model update must be recalculated at each iteration.
There are lots of examples of the effects of 3D structure on such kernels in the literature (see, for instance, Tape et al. 2007 for multi-pathing surface waves or in synthetic studies such as Koroni et al. 2017 to see the effect of superposition of multiple arrivals, etc.). However, thanks for the comment where we indeed want to study such observations in follow-up papers.}

@@

\rev{2. Along the same lines, do the sensitivity kernels for body waves through the deep mantle change from iteration 0 to 25? Always or only when, for example, when they skirt the LLSVP? Would it be sensible to recalculate the high-frequency body-wave kernels only every 5th or 10th iteration to safe computational time? Are there good reasons not to do this?
}

\response{See our response to the previous comment. We do not calculate individual sensitivity kernels a la Dahlen \& Nolet. We compute ``event kernels" for each event combining all body- and surface-wave measurements together. Even if one may argue that lower mantle kernels should be simple, D'' and upper mantle definitely not. For instance, multiply reflected body waves from the free surface can show complicated patterns as one can expect. Furthermore, even though the lower mantle portion might be relatively simple, the crustal and upper-mantle portion of the kernels may still be affected by strong heterogeneities. Overall it does not cost extra for us to run 3D kernels for body-wave phases sampling the lower mantle. 
%\fromebru{I think we can put such a figure as well (I mean in the response, not sure needed for the paper but may go into SOM as well). The kernels must definitely change for paths across the plumes. Also we may be able to give what I encountered in GLAD-M15 before taking full attenuation into account in adjoint simulations as an evidence that we need to compute exact kernels to further decrease the misfit and improve the model}
%\toebru{Going back to Carl and Qinya's papers, there are lots of such examples in the literature. There is no need to belabor this.}
}

@@

\rev{3. I would like to see examples of recorded and synthetic data at long (T > 250 s), and short (T < 10 s) periods to illustrate that M25 is (close to) reproducing waveform segments and data types not yet selected by FLEXWIN. How good is the fit to waveform segments (e.g., ScS) and data types (e.g., normal mode splitting) not included in the inversion?
}

\response{Calculating synthetics at periods less than 17 s is a very expensive proposition! Going to 9~s involves a 16X increase in the computational cost. The long period corner of the period band is set by the Cowling approximation,
which limits simulations to periods up to $\sim250--300$~s. However, all these suggestions can be good further smaller projects to be investigated.
}

@@

\rev{4. Source finiteness is already important. A MW7.2 earthquake is assumed to have a duration of 21 seconds (an empirically determined value in the CMT catalog) comparable to the shortest periods used here. What is the effect on the traveltime measurement if the duration is overestimated by 5 or 10 seconds (deep earthquakes tend be more compact)? When higher frequencies are incorporated, do the authors plan to invert for source durations or can they rely on standard catalogs of source time functions (e.g., SCARDEC)?
}

\response{Low pass filtering at 17~s largely eliminates sensitivity to shorter half durations. 
In addition, when the waveform difference caused by the source time function is too large, it will be rejected by our data screening process. Going forward we are planning to do our own CMT inversions in M25, but including an STF estimation.
}

\rev{5. As the authors plan to include attenuation in the parameterization, will this be a new 1-D profile for Q or a fully 3-D structure? How might this affect the inversion for dVs (and dVp)? For example, assuming that dVs and dQ-1 are related linearly ---- take Colleen Dalton's model for a first-order scaling between dVs and dQ-1 ---- how would this change the traveltime fits? How should dVs and dQ-1 be parameterized (and regularized) to assure that the inversion converges to sensible models for both parameters?
}

\response{We are planning a fully 3D Q inversion. This will be a ``proper'' Q inversion,
where the full effects of attenuation, i.e., physical dispersion and dissipation, will be taken into account and inverted simultaneously with the elastic parameters. We have some experience with such inversions in Europe (Zhu et al., 2013), and for problems in exploration seismology. We have also started experimenting at the global scale with the smaller dataset used in GLAD-M15. The reviewer is right that the Q model will directly affect the traveltimes;
all tomographic inversions are affected by this.
}

@@

\rev{f) Figure 3. This figure is fairly busy and not informative. If the authors decide to keep it, I suggest the oceans and continents are simply white.
}

\response{We like this figure, which gives a good idea of station `hit count'. It has been combined with the source figure.
}

\rev{g) Page 8. I have read the statement on SAC before in Jeroen's papers and I apologize for my quibble. The ASDF format may very well be ideal but there are options other than SAC. Many seismologists, including yours truly 20 years ago, developed data and metadata containers that are self-describing, compact, and ``cat-able'' to improve I/O and processing speeds. The bullets on page 9 are too vague.
}

\response{Point taken.  Indeed there has been other data formats similar to the ASDF logic before the ASDF. We emphasize ASDF because of its compatibility to HPC systems. We have removed the section on ASDF because the format is already discussed in the original ASDF paper, and in the Bozdag et al.~(2016) paper.}

@@

\rev{h) Page 9. It is not clear to me which part(s) of the seismogram the data categories encompass. Can waveform segments classified as ``17-40 s body waves'' overlap with segments from the ``40-100 s body waves'' group? It would be helpful to show four seismograms for the different frequency bands that indicate where windows are typically chosen.
}

\response{The windows are taken independently of categories, based on the quality of fit. The windows in different categories do not necessarily overlap. Examples of such windows may be found in Bozdag et al.~(2016).}

@@

\rev{i) Page 10. Was the imbalance in M15 (e.g., thousands of paths between circum-Pacific events and the USArray) the motivation for the source and receiver weights in equations 5 and 6?
}

\response{Yes. M15 tried to compensate for this based on a kernel density used as the preconditioner in our post-processing stage, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}

@@

\rev{j) Figure 6. Both PS and SP can be strong on the vertical and radial components. So, change the label ``PS'' to ``SP+PS''. Why are there few segments close to the PPP arrival (beyond 100 degrees)? Since it is used in the caption, I would use seconds along the y-axis (also in the next two figures).
}

\response{Points taken. PPP is not prominent, and picked rarely by Pyflex with conservative selection criteria to avoid bad-quality windows. In addition, to linearize our inversions, we do not select any window with large time shift and amplitude anomalies until observed and synthetic waveforms becomes comparable to make measurements. It is ongoing research to improve automated phase picking algorithms.}

@@

\rev{k) Figure 8. Why are there few segments along the SSS branch? I understand FLEXWIN does not look for ScS, ScS2, ScS3 etc. but one doesn't need to teach a machine to find them.
At T > 15 s periods they are very apparent for dip-slip earthquakes (especially deep earthquakes) and they are isolated from other phases at the shortest distances.
PcP is visible at D< 60 deg but it is otherwise a crappy phase. No one has ever found PcP2, as far as I know. Other phases to consider are the major-arc S reflections (i.e. SSm, SSSm). 
They propagate through the mantle in the southern hemisphere. We selected a few thousand but could not fit their traveltimes well (using ray theory).
}

\response{S and SS are more prominent than SSS, and Pyflex selects fewer of these arrivals mainly because of our conservative selection criteria. We are working on adjusting the Pyflex setting to specifically pick ScS, ScS2, and other later arrivals, so these will be better included in future iterations.}

@@

\rev{l) Table 1. Clarify ``changes in fit'' or maybe show residual misfit instead which is used frequently. Is it correct that the 40-100 s period surface wave fit has improved the most? This would indicate that the 10 iterations have primarily adjusted the uppermost mantle.
Is the misfit reduction smallest for the ``overtones surface waves'' (the S multiples arriving before the fundamental mode) (i.e., 40-100 s body waves)?
This might indicate that the mantle transition is still resolved poorly (or was already resolved very well by S362ANI).
Section 8.4 could use more discussion regarding the misfits of the various categories and what it implies for the resolution of dVs (and dVp) as a function of depth.
}

\response{This is the variance reduction for the subset of measurements in each of the 12 categories. Surface waves show more of a reduction because the waveforms are more complex, and moving them in phase gives a greater variance reduction than improving the fit to a simpler body waveform. The categories reflect pass bands and components, not depth resolution..}

\rev{m) Figure 10. The histograms of Figure 10 also suggest the modeling of the 40-100 s surface waves has been most successful. Maybe the overtones should have more weight in the next iterations?
}

\response{See the earlier explanation.
Surface wave fits are much worse than body wave fits prior to inversion, because the former waveforms are dispersed.
Thus there are more gains to be had. We don't strip overtones, so these are not fit individually, nor can they be weighted separately.
Instead, we fit full surface waveforms. However, we are working on new measurement techniques where higher modes and any scattered waves with smaller amplitudes can be better taken into account than cross-correlation measurements. See Bozdag et al. 2011 and the recent paper Yuan et al. 2020 for such measurements which we aim to incorporate in our future iterations. 
}

@@

\response{We removed these histograms and the amplitude histograms. However, we believe the slight skew is more likely related to depth phase, which skew the P and SH arrival and may bias the cross-correlation traveltime measurement.}

\rev{o) Figure 12. The discussion on amplitudes is also a bit brief and lacks citations to previous work (e.g., Dalton et al.).
I disagree that the ``histograms are nicely centered''. Some peaks are near -0.1 or -0.15 meaning that amplitude for some segments are, on average, 10-15\% lower than predicted. I have recorded discrepancies in the SS/S amplitude ratio by the same amount.
This ratio is insensitive to the source. I would be curious to hear what the data set used here finds for SS/S.
}

\response{We are not sure what you mean. The M25 peaks in Fig.~12 are at 0.02, -0.01, 0.02, -0.05, -0.03, -0.04, 0.05, 0.10, -0.06, -0.02, 0.07, and -0.06. So only one peak is at -0.1, and considering the standard deviations, these histograms really are ``nicely centered''.
Note that the amplitude histograms were removed in the interest of succinctness and focus.}

\rev{p) Page 26 and Figure 16. The authors must include panels for M15 in Figure 16 and discuss what has changed.
Given the variance reductions I suspect most adjustments have been made in the upper mantle. }

\response{We have now added comparison of M25 to M15 in the revised manuscript and in the SOM.}

\rev{(i) Although the authors invert for dVp and dVs, the resolution of dVp is poorer than of dVs, particularly in the uppermost mantle (constrained by surface waves) and in D'' (constrained by diffracted waves).}

\response{Not sure if this is a general comment for seismic tomography or for our models. S-wave perturbations are in general larger than those of P waves. It is also likely that we have less P-wave measurements than S-wave measurements because of the smaller amplitudes of P waves. Therefore P-wave evolution can be slower than that of S waves. The smoother P-wave model of GLAD-M25 compared to other P-wave models is also likely due to our minimum period of body waves which is 17~s.}

### 2020-02-19 supplementary_material.tex
Updates from Overleaf

Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
To improve the sampling of the thin oceanic crust the mesh honors Moho whenever the crust is thinner than 15~km and thicker than 35~km. The mesh runs through the GLL (Gauss-Lobatto-Legendre) points at the ocean-continent transition (15--35~lm crustal thickness) as described in \citet{tromp2010a}. The mantle and crust are inverted simultaneously avoiding any simplifications and crustal corrections.

GLAD-M15 was constructed using a global database of 253 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s. Note that the shortest period of simulations is most crucial for taking advantage of high-frequency body waves since the minimum period of surface waves we currently fit in adjoint inversions is 40~s.

@@

Before using the 1,040 earthquakes in our structural inversion,
we performed CMT inversions using model GLAD-M15, similar to the 253 events reinverted in \citet{bozdaug2016global} using its starting model S362ANI+CRUST2.0,
the results of which are summarized in Fig.~\ref{fig:source_correction}.
To optimize even global coverage,
we used seismographic stations from the  Global Seismic Network (II, IU, IC, US, CU, and GT),
GEOFON~(GE), GEOSCOPE~(G), and several regional networks, such as MedNet~(MN),
the Brazilian Lithospheric Seismic Project~(BL), the Chilean National Seismic Network~(C),
and the Japan Meteorological Agency Seismic Network~(JP) (Fig.~\ref{fig:source_correction}b).
The number of stations used for CMT inversion usually ranges
from~150 to~500 depending on the event dates.

To update the source parameters (six moment tensor components, latitude, longitude and depth) using the starting model to compute the Green's functions for each source parameter,
we used the CMT inversion algorithm of \cite{liu2004spectral}.
This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
Specifically, the algorithm minimizes the misfit function
\begin{equation}
   \begin{split}
      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
          & \left\{ \lambda\, \frac
              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
              \quad ,
   \end{split}
\end{equation}
where~$d_w(t)$ denotes data in time window~$w$\,,
and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
We allow the synthetics to shift relative to the data by an amount~$\Delta t$
--- effectively a station correction --- determined by cross correlation. We do not invert for the origin times as we minimize the phase misfit due to the station correction which helps to reduce the nonlinearity of the problem. As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
The envelope function is denoted by~$e(\,\cdot\,)$\,,
and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
The number of measurement categories is denoted by~$C$\,.
Following~\cite{ekstrom2012global},
seismograms were filtered between 50~s and 100~s
to select three-component body-wave windows,
and between 60~s and 100~s to select three-component
surface-wave windows,
resulting in six measurement categories, $c=1,\ldots,C$\,.
To balance their contributions,
each category is weighted by the reciprocal of the number of measurements in that
category, $\omega_c$\,.
The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
As shown in Fig.~\ref{fig:source_correction}b,
the receivers are unevenly distributed across the globe,
with several dense arrays in the northern hemisphere and poor coverage in the southern hemisphere.
To balance the coverage,
following a strategy articulated by~\cite{Ruanetal2018},
we assign receiver weights~$\omega_{cr}$ based on the expression
\begin{equation}
\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
\quad ,
\label{eq:spatial_weights}
\end{equation}
where~$N_c$ is a normalization factor for category~$c$,
and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
The calculation of the weights may be abstracted as: given a distribution of
points on the unit sphere, determine a spatial weighting associated with each point.

@@

Most earthquakes, specifically the oceanic ridge events, are shallower after inversion
(Fig.~\ref{fig:source_correction}c),
consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}. This is partly because the minimum depth of CMT events are fixed to $\sim12$~km as the sensitivity of source parameters significantly decreases closer to the free surface. 
We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
an average scalar moment change of~$5.31\pm3.91$\%,
and an average centroid time shift of~$-0.60\pm1.17$~s.
These are relatively minor corrections mainly due to our choice of being conservative in source inversions to avoid nonlinearities and our not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
For this reason, when we added another 440 earthquakes during iteration~22,
thereby bringing the total to~1,480 events,
we only performed a grid search to calibrate the centroid times and scalar moments.

@@

The forward simulations are based on the global spectral-element solver
SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a list
of stations, and the current earth model as input.
The solver is GPU accelerated, and the simulations are performed on the Cray ``Titan'' and IBM ``Summit" supercomputers
at the OLCF.
To simulate 120-min seismograms with a shortest period of 17~s on 384 NVIDIA
Tesla K20X GPUs takes approximately 10~min of wall clock time (On Summit it takes about \cyan{1~min (??)}).

@@

As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow
includes the following phases.
\begin{enumerate}
  \item Signal processing to remove the instrument response from observed data
    to recover ground displacement using ObsPy~\citep{obspy2010}. Both observed and synthetic data are filtered using the same bandpass only once, and the horizontal components are rotated to obtain the radial and transverse components of motion.
  \item Window selection on a pair of
    observed and synthetic seismograms. Pyflex (a Python version
    of FLEXWIN by \citet{krischer2015}) is
    used to automatically generate windows where observed and
    synthetic data are sufficiently close to make measurements based on user defined
    criteria.
  \item Cross-correlation traveltime or multi-taper phase measurements in selected windows.
  \item Window sorting and cleaning based on statistical analyses of all measurements to eliminate outliers.
  \item Preliminary adjoint source construction based on the sorted windows.
  \item Calculation and assignment of source and receiver weights~\citep{Ruanetal2018}.
  \item Construction of the final, properly weighted, adjoint sources.
\end{enumerate}

@@

Collectively,
the adjoint simulations are the most expensive stage of the workflow. 
Adjoint simulations take the adjoint sources as input, and generate Fr\'echet
derivatives of the four model parameters as output.
The computational cost of one adjoint simulation is roughly twice ($\sim25$~min on Titan, \cyan{less than $10$~min on Summit}) that of
a forward simulation, since the forward wavefield is recalculated for convolution with
the adjoint wavefield during the adjoint simulation.
Using this procedure,
both the forward and adjoint wavefields are calculated in forward time,
and attenuation is accurately taken into account in both simulations \citep{KoXiBoPeSaLiTr16}.

>>>>

Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
To improve the sampling of the thin oceanic crust the mesh honors the Moho whenever the crust is thinner than 15~km and thicker than 35~km. The mesh runs through the GLL (Gauss-Lobatto-Legendre) points at the ocean-continent transition (15--35~km crustal thickness) as described in \citet{tromp2010a}. The mantle and crust are inverted simultaneously,
thereby avoiding any simplifications or crustal corrections.

GLAD-M15 was constructed using a global database of 253 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s. Note that the shortest period of the simulations is most crucial for taking advantage of high-frequency body waves, since the minimum surface-wave period we currently fit is 40~s.

@@

Before using the 1,040 earthquakes in our structural inversion,
we performed CMT inversions using model GLAD-M15, similar to the 253 events reinverted in the \citet{bozdaug2016global} study using its starting model S362ANI+CRUST2.0,
the results of which are summarized in Fig.~\ref{fig:source_correction}.
To optimize even global coverage,
we used seismographic stations from the  Global Seismic Network (II, IU, IC, US, CU, and GT),
GEOFON~(GE), GEOSCOPE~(G), and several regional networks, such as MedNet~(MN),
the Brazilian Lithospheric Seismic Project~(BL), the Chilean National Seismic Network~(C),
and the Japan Meteorological Agency Seismic Network~(JP) (Fig.~\ref{fig:source_correction}b).
The number of stations used for CMT inversion usually ranges
from~150 to~500 depending on the event dates.

To update the source parameters (six moment tensor components, latitude, longitude and depth) using the starting model to compute the Green's functions for each source parameter,
we used the CMT inversion algorithm of \cite{liu2004spectral}.
This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
Specifically, the algorithm minimizes the misfit function
\begin{equation}
   \begin{split}
      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
          & \left\{ \lambda\, \frac
              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
              \quad ,
   \end{split}
\end{equation}
where~$d_w(t)$ denotes data in time window~$w$\,,
and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
We allow the synthetics to shift relative to the data by an amount~$\Delta t$
--- effectively a station correction --- determined by cross correlation. We do not invert for the origin times as we minimize the phase misfit due to the station correction, which helps to reduce the nonlinearity of the problem. As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
The envelope function is denoted by~$e(\,\cdot\,)$\,,
and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
The number of measurement categories is denoted by~$C$\,.
Following~\cite{ekstrom2012global},
seismograms were filtered between 50~s and 100~s
to select three-component body-wave windows,
and between 60~s and 100~s to select three-component
surface-wave windows,
resulting in six measurement categories, $c=1,\ldots,C$\,.
To balance their contributions,
each category is weighted by the reciprocal of the number of measurements in that
category, $\omega_c$\,.
The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
As shown in Fig.~\ref{fig:source_correction}b,
the receivers are unevenly distributed across the globe,
with several dense arrays in the northern hemisphere and poor coverage in the southern hemisphere.
To balance the coverage,
following a strategy articulated by~\cite{Ruanetal2018},
we assign receiver weights~$\omega_{cr}$ based on the expression
\begin{equation}
\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
\quad ,
\label{eq:spatial_weights}
\end{equation}
where~$N_c$ is a normalization factor for category~$c$,
and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
The calculation of the weights may be abstracted as: given a distribution of
points on the unit sphere, determine a spatial weighting associated with each point.

@@

Most earthquakes, specifically oceanic ridge events, are shallower after inversion
(Fig.~\ref{fig:source_correction}c),
consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}. This is partly because the minimum depth of CMT events is fixed to $\sim12$~km, because the sensitivity of source parameters significantly decreases closer to the free surface. 
We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
an average scalar moment change of~$5.31\pm3.91$\%,
and an average centroid time shift of~$-0.60\pm1.17$~s.
These are relatively minor corrections, mainly due to being conservative in the source inversions to avoid nonlinearities and the not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
For this reason, when we added another 440 earthquakes during iteration~22,
thereby bringing the total to~1,480 events,
we only performed a grid search to calibrate the centroid times and scalar moments.

@@

The forward simulations are based on the global spectral-element solver
SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a}, and take a CMT solution, a list
of stations, and the current earth model as input.
The solver is GPU accelerated, and the simulations are performed on the Cray ``Titan'' and IBM ``Summit" supercomputers
at the OLCF.

@@

As illustrated in Fig.~\ref{fig:preprocess_workflow}, the preprocessing workflow
includes the following phases.
\begin{enumerate}
  \item Signal processing to remove the instrument response from observed data
    to recover ground displacement using ObsPy~\citep{obspy2010}. Both observed and synthetic data are filtered using the same bandpass, and the horizontal components are rotated to obtain the radial and transverse components of motion.
  \item Window selection on a pair of
    observed and synthetic seismograms. Pyflex (a Python version
    of FLEXWIN by \citet{krischer2015}) is
    used to automatically generate windows where observed and
    synthetic data are sufficiently close to make measurements based on user defined
    criteria.
  \item Cross-correlation traveltime or multi-taper phase measurements in selected windows.
  \item Window sorting and cleaning based on statistical analyses of all measurements to eliminate outliers.
  \item Preliminary adjoint source construction based on the sorted windows.
  \item Calculation and assignment of source and receiver weights~\citep{Ruanetal2018}.
  \item Construction of the final, properly weighted, adjoint sources.
\end{enumerate}

@@

Collectively,
the adjoint simulations are the most expensive stage of the workflow. 
Adjoint simulations take the adjoint sources as input, and generate Fr\'echet
derivatives of the four model parameters as output.
The computational cost of one adjoint simulation is roughly twice ($\sim25$~min on Titan, less than $10$~min on Summit) that of
a forward simulation, since the forward wavefield is recalculated for convolution with
the adjoint wavefield during the adjoint simulation.
Using this procedure,
both the forward and adjoint wavefields are calculated in forward time,
and attenuation is accurately taken into account in both simulations \citep{KoXiBoPeSaLiTr16}.
